SSA based global code motion of identical computations

### 2017-04-17 paper.tex
less sinks

Loads are hoisted the most followed by scalars, stores and calls in decreasing
order.  This was the common trend in all our experiments. One reason why loads
are hoisted the most is the early execution of this pass (before mem2reg) in the
\LLVM{} pass pipeline. Passes like mem2reg, instcombine might actually remove
those loads so this order may change should this pass be scheduled later.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|r|r|r|r|r|r|r|r|}
      \hline
 code-motion      & Instructions&Instructions   & Loads	        &Loads	        &Stores &Stores &Calls &Instructions \\\hline
 metric           &  hoisted    &removed	&hoisted        &removed        &hoisted&removed&hoisted & sunk     \\\hline
 400.perlbench	  &  2387	& 2456		& 1493		& 1560		& 38	& 38	& 1	& 4	       \\\hline
 401.bzip2	  &  176	& 300		& 149		& 273		& 0	& 0	& 0 	& 0		\\\hline
 403.gcc	  &  5670	& 5761		& 3109		& 3191		& 3	& 3	& 0	& 1	       \\\hline
 429.mcf	  &  42	        & 43		& 37		& 38		& 0	& 0	& 0 	& 0		\\\hline
 433.milc	  &  128	& 130		& 117		& 119		& 0	& 0	& 1	& 0		\\\hline
 444.namd	  &  262	& 264		& 148		& 150		& 0	& 0	& 1	& 0		\\\hline
 445.gobmk	  &  1021	& 1052		& 705		& 734		& 3	& 3	& 1	& 1	       \\\hline
 447.dealII	  &  10455	& 12325		& 6394		& 8210		& 20	& 20	& 32	& 0	       \\\hline
 450.soplex	  &  2389	& 2731		& 1437		& 1702		& 14	& 14	& 11	& 0	       \\\hline
 453.povray	  &  1967	& 2269		& 1389		& 1661		& 4	& 4	& 14	& 0	       \\\hline
 456.hmmer	  &  408	& 427		& 319		& 338		& 1	& 1	& 6	& 0	       \\\hline
 458.sjeng	  &  372	& 399		& 234		& 251		& 1	& 1	& 9	& 1	       \\\hline
 462.libquantum	  &  49	        & 49		& 32		& 32		& 0	& 0	& 0	& 0		\\\hline
 464.h264ref	  &  2953	& 3438		& 2238		& 2656		& 2	& 2	& 1	& 1	       \\\hline
 470.lbm	  &  23	        & 23		& 19		& 19		& 0	& 0	& 0	& 0		\\\hline
 471.omnetpp	  &  391	& 408		& 297		& 314		& 0	& 0	& 2	& 0		\\\hline
 473.astar	  &  202	& 222		& 140		& 158		& 0	& 0	& 0	& 0		\\\hline
 482.sphinx3	  &  168	& 172		& 136		& 140		& 0	& 0	& 0	& 0		\\\hline
 483.xalancbmk	  &  5894	& 6162		& 3301		& 3495		& 4	& 4	& 3	& 2	       \\\hline
    \end{tabular}
  \end{center}
  \caption{Code motion stats on SPEC2006 at -Ofast}
  \label{tab:code-motion-metric}
\end{table}

>>>>

Loads are hoisted the most followed by scalars, stores and calls in decreasing
order.  This was the common trend in all our experiments. One reason why loads
are hoisted the most is the early execution of this pass (before mem2reg) in the
\LLVM{} pass pipeline. Passes like mem2reg, instcombine might actually remove
those loads so this order may change should this pass be scheduled later. The number
of instructions sunk is very less because \LLVM{} has a code sinking pass inside SimplifyCFG
which is run before the global code-motion and sinks some instructions. Another reason is
that instructions for which dependencies are not directly available in the successor is
not sunk for now. Sinking those instructions would require a look ahead on the sinkability
of the dependencies. We plan to implement this in near future.

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{|l|r|r|r|r|r|r|r|r|r|}
      \hline
 code-motion  &\multicolumn{2}{|c|}{Total Instructions} &\multicolumn{2}{|c|}{Scalars}  & \multicolumn{2}{|c|}{Loads} & \multicolumn{1}{|c|}{Stores} &Calls   &Instructions    \\\hline
 metric           &  hoisted    &removed  &hoisted &removed&hoisted     &removed        &hoisted=removed&hoisted & sunk \\\hline
 400.perlbench	  &  2387	& 2456	  &  855  & 857	   & 1493	& 1560		& 38	& 1	& 4	        \\\hline
 401.bzip2	  &  176	& 300	  &  27	  & 27	   & 149	& 273		& 0	& 0 	& 0		\\\hline
 403.gcc	  &  5670	& 5761	  &  2558 & 2567   & 3109	& 3191		& 3	& 0	& 1	        \\\hline
 429.mcf	  &  42	        & 43	  &  5	  & 5	   & 37 	& 38		& 0	& 0 	& 0		\\\hline
 433.milc	  &  128	& 130	  &  10	  & 10	   & 117	& 119		& 0	& 1	& 0		\\\hline
 444.namd	  &  262	& 264	  &  113  & 113	   & 148	& 150		& 0	& 1	& 0		\\\hline
 445.gobmk	  &  1021	& 1052	  &  312  & 314	   & 705	& 734		& 3	& 1	& 1	        \\\hline
 447.dealII	  &  10455	& 12325	  &  4009 & 4063   & 6394	& 8210		& 20	& 32	& 0	        \\\hline
 450.soplex	  &  2389	& 2731	  &  927  & 1004   & 1437	& 1702		& 14	& 11	& 0	        \\\hline
 453.povray	  &  1967	& 2269	  &  560  & 590	   & 1389	& 1661		& 4	& 14	& 0	        \\\hline
 456.hmmer	  &  408	& 427	  &  82	  & 82	   & 319	& 338		& 1	& 6	& 0	        \\\hline
 458.sjeng	  &  372	& 399	  &  128  & 138	   & 234	& 251		& 1	& 9	& 1	        \\\hline
 462.libquantum	  &  49	        & 49	  &  17	  & 17	   & 32	      	& 32		& 0	& 0	& 0		\\\hline
 464.h264ref	  &  2953	& 3438	  &  712  & 779	   & 2238	& 2656		& 2	& 1	& 1	        \\\hline
 470.lbm	  &  23	        & 23	  &  4	  & 4	   & 19		& 19		& 0	& 0	& 0		\\\hline
 471.omnetpp	  &  391	& 408	  &  92	  & 92	   & 297	& 314		& 0	& 2	& 0		\\\hline
 473.astar	  &  202	& 222	  &  62	  & 64	   & 140	& 158		& 0	& 0	& 0		\\\hline
 482.sphinx3	  &  168	& 172	  &  32	  & 32	   & 136	& 140		& 0	& 0	& 0		\\\hline
 483.xalancbmk	  &  5894	& 6162	  &  2586 & 2660   & 3301	& 3495		& 4	& 3	& 2	        \\\hline
 Grand total      &34957	&38631	  &13091  &13418   &21694	&25041	        &90	&82     &10             \\\hline
    \end{tabular}
  \end{center}
  \caption{Code motion stats on SPEC2006 at -Ofast}
  \label{tab:code-motion-metric}
\end{table}
